---
title: "Homework 1"
author : Siddarth Arumugam
date: September 2020
output: github_document
---

This is my solution to HW1

```{r message = FALSE}
library(tidyverse)
```

## Problem 1

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp) 
```


## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
head(penguins)
```
The dataset has column names that are [`r names(penguins)`]. The dataset represents the different species of penguins and their physical attributes (bill length in mm, bill depth in mm, flipper length in mm, body mass index, sex) and the islands they are found on. The dataset has `r length(unique(penguins[["species"]]))` species of penguins found on `r length(unique(penguins[["island"]]))` islands.


The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length in mm is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(na.rm = TRUE, aes(color = species, shape = species), size = 2.5)
ggsave(filename = 'Scatter_Plot.pdf', plot = last_plot(), dpi = 600)
```

