---
title: "Homework 1"
author : Siddarth Arumugam
date: September 2020
output: github_document
---

This is my solution to HW1

```{r message = FALSE}
library(tidyverse)
```

## Problem 1

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

### Taking the mean of each variable in the data frame

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

The means of numbers and logical are valid but not for characters or factors


### Type conversion
```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
It is possible to convert numbers and logical values to their numeric equivalents. The factor variable is converted into the numberical equivalent of the 3 grades. Trying to convert the character vector throws an error. 

### Type conversion and multiplying with the random sample
```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp) 
```
Converting the logical vector to a numeric made it possible to multiply it with the random sample. Converting it to a factor, however resulted in an error when multiplying with the random sample. Converting the factor to a numeric allowed the arithmetic operation. 

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
head(penguins)
```
The dataset has column names that are [`r names(penguins)`]. The dataset represents the different species of penguins and their physical attributes (bill length in mm, bill depth in mm, flipper length in mm, body mass index, sex) and the islands they are found on. The dataset has `r length(unique(penguins[["species"]]))` species of penguins found on `r length(unique(penguins[["island"]]))` islands.


The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length in mm is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(na.rm = TRUE, aes(color = species, shape = species), size = 2.5)
ggsave(filename = 'Scatter_Plot.pdf', plot = last_plot(), dpi = 600)
```

